---
title: "MA 415/615 Homework 2"
author: "**`[==[`** Your Name **`]==]`**"
output: html_document
---

In this homework, we're performing a more detailed analysis of the `nycflights13` dataset we saw in lecture. This data set contains flight information from all flghts that departed NYC in 2013. We start by loading the packages:

```{r init}
library(tidyverse)
library(nycflights13)
```

**`[==[`** Note: instructions are framed with bold `[==[` and `]==]` and should be either removed (like this one!) or substituted by answers in the final version of your document. **`]==]`**


## Question 1

Here are the top 4 carriers in total number of flights departing NYC in 2013:

**`[==[`** Change the `q1` chunk to create a dataset with only the top **4** carriers in total number of flights, then store these carriers in variable `big_carriers`. Recall that `dataset$variable` extracts `variable` values from `dataset`. **`]==]`**

```{r q1}
unique(flights$carrier) # all carriers
(big_carriers <- c("AA", "UA", "DL"))
```


## Question 2

Here are the proportion of canceled flights for the top 4 carriers at each origin airport:

**`[==[`** Change the `q2` chunk to compute the proportion of canceled flights for each top carrier and origin, and arrange them by origin and decreasingly by proportion. A cancelled flight has missing data for arr_delay or dep_delay. **`]==]`**

```{r q2}
flights %>% filter(carrier %in% big_carriers) %>%
  group_by(origin, carrier) %>%
  summarize(prop_delayed = mean(between(dep_delay, 0, 30), na.rm = TRUE))
```

**`[==[`** Comment on the proportions and if some carrier seems to cancel more often depending on the origin airport. **`]==]`**


## Question 3

To investigate if there is any pattern of flight cancellations depending on the time of year, I first create a `canceled_by_doy` dataset with the proportion of canceled flights for each day of the year (`doy`) and `origin`:

**`[==[`** Change the `q3` chunk to create the `canceled_by_doy` dataset as described above, but keep the definition of `doy`. Use `?` in R to determine what exctly `doy` is and how it is created. **`]==]`**

```{r q3}
flights %>% transmute(doy = as.integer(strftime(time_hour, format = "%j")))
```


## Question 4

**`[==[`** Create a new `q4` chunk that uses `canceled_by_doy` to plot the proportions of canceled flights for each day of the year; color the points by `origin` and with alpha transparency of 0.3. Add a colored smoother for each origin, but without the confidence bands. **`]==]`**

```r
# `q4` here
```

**`[==[`** Comment on overall shape of curves and unusual days. **`]==]`**
