---
title: "MA 415/615 Homework 5"
author: "**`[==[`** Your Name **`]==]`**"
output: html_document
---

## Question 1

In this work I'll analyze the titles of papers presented at the NIPS
conference from 1987 to 2017. The data in file `nips-titles.csv`, loaded into
table `papers`, contains only two columns, `year` and `title` from the
[original Kaggle dataset](https://www.kaggle.com/benhamner/nips-papers).
As an initial check, I'm plotting the distribution of the number of words in a title
for each year.


**`[==[`**
Modify the `q1` chunk below to load the needed libraries and load
`nips-titles.csv` into dataset `papers`. The data set is on Blackboard. Check that `papers` has no problems.
Now create a new variable `word_count` with the number of words in each title. Then make boxplots of the number of words per title for each year. Write a
short assessment about the variability of title sizes over the years.
**`]==]`**

```{r q1}
library(tibble) # just a placeholder, should be removed
library(tidyr) # just a placeholder, should be removed
```

## Question 2

**`[==[`**
Modify chunk `q2` below to "cross" each title in `papers` with each keyword in
`keywords`(your code should start with `papers %>% crossing(keywords)`; use the example below), then check if each title contains each keyword. Before
checking, however, convert the words in the title to lower case since the
keywords are all in lower case. Store the outcome of the check in a new variable called `keyword_in_title`: it should be `FALSE` if the keyword
is absent and `TRUE` if present in the title. Then, for each year and keyword, count how many titles (in a new condensed data set)
contain the keyword in the year, and store in variable `n`. (**Hint**: using `count` with `wt = ` a logical vector will sum the `TRUE`'s) Finally, using `spread`,
cross-tabulate these counts for the last ten years by indexing rows by year
and columns by keyword. Your final table should look like this after using `%>% tail(n = 10)`:

```{r q2-info, echo = FALSE}
tribble(
  ~year, ~bayesian, ~data, ~deep, ~learning, ~models, ~networks, ~neural, ~optimization, ~stochastic,
  2008L, 13L,       11L,   1L,    51L,       22L,     10L,       7L,      6L,            4L,         
  2009L, 20L,       9L,    4L,    61L,       24L,     6L,        7L,      7L,            6L,         
  2010L, 12L,       14L,   3L,    65L,       19L,     14L,       8L,      9L,            5L,         
  2011L, 9L,        15L,   3L,    79L,       25L,     9L,        11L,     10L,           10L,        
  2012L, 22L,       12L,   10L,   92L,       31L,     15L,       14L,     12L,           8L,         
  2013L, 20L,       18L,   13L,   77L,       33L,     18L,       17L,     17L,           17L,        
  2014L, 18L,       20L,   22L,   85L,       41L,     25L,       28L,     16L,           15L,        
  2015L, 16L,       16L,   21L,   78L,       36L,     33L,       22L,     31L,           22L,        
  2016L, 23L,       24L,   44L,   121L,      43L,     64L,       47L,     39L,           38L,        
  2017L, 20L,       35L,   64L,   180L,      38L,     69L,       64L,     29L,           25L
)
```
**`]==]`**

```{r q2}
keywords <- tibble(keyword = c("bayesian", "data", "deep", "models",
              "networks", "neural", "learning", "optimization", "stochastic")) # keep and use this!
# example of crossing between two tables:
crossing(tibble(x = 1:3), tibble(y = letters[1:3]))
```


## Question 3

**`[==[`**
It's hard to assess counts in a table, so, in a chunk labeled `q3`, make a
line plot of the keyword counts vs year with one line for each keyword
(color each line by keyword). (**Hint**: use your code in Question 2 up until the point where you use `spread`. This data set should be used to make the plot) Comment on any specific patterns; for instance,
what seems to be the most popular keyword? Any keywords declining or
increasing in popularity over time?
**`]==]`**


## Question 4

**`[==[`**
The counts for some keyword can be increasing simply because the number of
conference papers is increasing with the years. Thus, instead of plotting
counts, make line plots of the **proportion** of papers in each year that had
each keyword in their titles. To this end, in a `q4` chunk, first create a new
dataset called `papers_year` with the counts of the number of papers per year and
then **join** this data set by variable `year` with the title-keyword crossed dataset in Question 2 (again, use the data set made in Question 2 just prior to using `spread`). Then
compute a new variable called `prop` with the proportion of titles containing
each keyword by year. Finally, create the plot. Do your conclusions change
when compared to the plot in Question 3? Comment.
**`]==]`**
